---
title: "twelfth"
author: "rita"
date: "2023-04-01"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggplot2)
```

## **Weight and MPG of Cars**

```{r 1.1}
cor.test(mtcars$wt, mtcars$mpg)


```

The two variables, weight and mpg, have a strong negative relationship as evident from both the Pearson test (above) and the graph (below).

A Pearson test correlation that is close to -1 is evident of a strong negative relationship and these two factors got a -0.87.

And as seen on the graph weight visibly increases mpg goes down. 

```{r 1.2 , echo=FALSE}
#mpg and wt
ggplot(mtcars, aes(x=wt, y=mpg)) +
  geom_point()+
  geom_smooth(method=lm, se=FALSE) +
  labs( title="Weight and MPG of Cars",
        y= "Miles per Gallon",
        x= "Weight (1000 lbs)")

```

## **Weight, MPG, and Type of Engine of Cars**


```{r 2.1}
cor.test(mtcars$mpg, mtcars$vs)
```


MPG and engine shape have a moderate to strong positive relationship as evident from both the Pearson test and the graph.

The Pearson test correlation close to 1 is evident of a strong positive relationship, but this is only a .66 which is a little over halfway there.

Cars with a higher mpg tend to have straight shaped engine. That can be easily seen on the graph as the upper half the y-axis tends to just be straight shaped. But there is a good mix of both in the middle. 

```{r 2.2}
cor.test(mtcars$wt, mtcars$vs)
```

Weight and engine shape have a moderate negative relationship as evident from both the Pearson test and the graph.

The Pearson test correlation close to -1 is evident of a strong negative relationship, but this is only a -.55.

Heavier cars tend to have v-shaped engine. That can be easily seen on the graph as from 3.5 down on the x-axis tends to just be v-shaped. But there is a good mix of both in the middle. 

```{r 2.3, echo=FALSE}
#mpg wt and vs
ggplot(mtcars, aes(x=wt, y=mpg, shape=as.factor(vs), color=as.factor(vs))) +   
  geom_point()+
  geom_smooth(method=lm, se=FALSE)+
  labs( title="Weight, MPG, and Type of Engine of Cars",
        y= "Miles per Gallon",
        x= "Weight (1000 lbs)")+
  scale_colour_discrete(name  ="Type of Engine",
                        breaks=c("0", "1"),
                        labels=c("V-shaped", "Straight")) +
  scale_shape_discrete(name  ="Type of Engine",
                       breaks=c("0", "1"),
                       labels=c("V-shaped", "Straight"))
```


